Matching Bullets

### 2015-12-11 imaging-paper.Rnw
Add question
iadded references

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item Smooth the two crosscuts by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to find the best alignment along the crosscuts: Shift one of the crosscuts by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, identify peaks and grooves for each of the crosscuts. We define a region around the extrema on each side as one third of the distance to the next extrema (see Figure~\ref{fig:smoothcutb}). 
\item Match grooves and peaks between crosscuts: based on the regions around the extrema as defined above, we identify joint regions between two crosscuts as those areas, in which at least two of the individual regions touch. A joint region is defined as the smallest interval that covers all of the touching regions. A joint region is called a match between the crosscuts, if all of the crosscut-specific regions are of the same type of extrema, i.e.\ either all peaks or all valleys. In Figure~\ref{fig:match} all matches are colored corresponding to their type of extrema. Non-matching regions are left grey.
\item Identify the maximal number of CMS (consecutive matching striae) between the two crosscuts by counting consecutive matching lines. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti~\cite{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match, and which are part of current practice in assessing bullet matches ~\cite{nichols:1997, nichols:2003}.
\end{enumerate}

@@

By suggesting an automated algorithm that first identifies lands, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. [T]`he concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner'~\cite{miller:1998}.
For a fair assessment of the adequacy of an algorithm we need transparency. Our matching  algorithm is open: the code is readily available in form of the R package x3rplus~\cite{x3prplus}, and the code to produce this paper is available at \hh{XXX, Eric ... we need a website}. Obviously, this is only a first step, but in times of the Netflix challenge and the many Data Science challenges hosted by Kaggle, we should not let the quality of the matching algorithm be the problem that stands in the way.

>>>>

All of the other steps are done on pairs of bullet lands:
\begin{enumerate}
\item Smooth the two crosscuts by a loess with a very small span (see Figure~\ref{fig:smooth}). 
\item Use cross-correlation to find the best alignment along the crosscuts: Shift one of the crosscuts by the lag indicated by the cross-correlation function (see Figure~\ref{fig:ccf} for the cross-correlation function and Figure~\ref{fig:crosscutX} for the resulting shift).
\item Using a rolling average, identify peaks and grooves for each of the crosscuts. We define a region around the extrema on each side as one third of the distance to the next extrema (see Figure~\ref{fig:smoothcutb}). 
\item Match grooves and peaks between crosscuts: based on the regions around the extrema as defined above, we identify joint regions between two crosscuts as those areas, in which at least two of the individual regions touch. A joint region is defined as the smallest interval that covers all of the touching regions. A joint region is called a match between the crosscuts, if all of the crosscut-specific regions are of the same type of extrema, i.e.\ either all peaks or all valleys. In Figure~\ref{fig:match} all matches are colored corresponding to their type of extrema. Non-matching regions are left grey.
\item Identify the maximal number of CMS (consecutive matching striae) between the two crosscuts by counting consecutive matching lines. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti~\cite{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match, and which are part of current practice in assessing bullet matches~\cite{nichols:1997, nichols:2003, nichols:2003b}.
\end{enumerate}

@@

By suggesting an automated algorithm that first identifies lands, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. [T]`he concept of counting striations is subjective and based on experience, but it does tend to be consistent within a single examiner'~\cite{miller:1998}.
For a fair assessment of the adequacy of an algorithm we need transparency. Our matching  algorithm is open: the code is readily available in form of the R package x3rplus~\cite{x3prplus}, and the code to produce this paper is available at \hh{XXX, Eric ... we need a website} \eh{XXX can we just put the GitHub link here?} \hh{github is fine!}. Obviously, this is only a first step, but in times of the Netflix prize~\cite{koren:2009, toescher:2009, piotte:2009} and the many Data Science challenges hosted by Kaggle, we should not let the quality of the matching algorithm be the problem that stands in the way.
